---
title: "R Notebook"
output: html_notebook
---

# Question 1
Read the cleaned data into R.
```{r}
library(tidyverse)
meteorite_landings <- read_csv("../clean_data/meteorite_landings_clean_kg.csv")
head(meteorite_landings)
```

# Question 2
Find the names and years found for the 10 largest meteorites in the data
```{r}
meteorite_landings %>%
  filter(fall == "Found") %>%
  slice_max(mass_g, n = 10, with_ties = FALSE)
```

# Question 3
Find the average mass of meteorites that were recorded falling, vs. those which were just found.


```{r}
meteorite_landings %>%
  group_by(fall) %>%
  summarise(avg_mass_g = mean(mass_g))
```

# Question 4
Find the number of meteorites in each year, for every year since 2000

```{r}
meteorite_landings %>%
  filter(year >= 2000) %>%
  group_by(year) %>%
  summarise(no_of_meteorites_found = n())
```

# Extension 
Using bboxfinder I was able to find the latitude and longitude for the continent and create a case when which took   the latitude and longitude from the meteorite findings and categorized this into their continents. I then used this information to create a function to show this information 
```{r}

source("../functions/show_continent_function.R")

show_continent(TRUE, -105.43333)
```

```{r}
meteorite_landings <- meteorite_landings %>%
  mutate(continent = show_continent(latitude, longitude))

meteorite_landings
```

# Number of meteorites per continent 
```{r}
meteorite_landings %>%
  group_by(continent) %>%
  summarise(count = n())
```

```{r}
meteorite_landings <- meteorite_landings %>%
  mutate(mass_kg = mass_g / 1000, .after = mass_g)

head(meteorite_landings)
```
# Top mteroites by continent
```{r}
meteorite_landings %>%
  group_by(continent) %>%
  slice_max(mass_kg, n = 1, with_ties = FALSE)
```
