---
title: "R Notebook"
output: html_notebook
---

# Day 2 Homework

The data for this homework comes from an Open Data Science website called Kaggle. Kaggle has many open source datasets for you to use and most of them come with code uploaded by other users showing different ways to explore the data. It is a great way to learn about data-wrangling and analysis and if you are interested then set up your own account and get going.

For this task we will make use of their Starbucks Calorie dataset. You can find out more information about each dataset and what each column represents , but we have put the version you need in your data folder.

## Question 1
Load in the dataset and have a look at it. What are the dimensions, variable types, variable names, etc.?

```{r}
library(tidyverse)
```

```{r}
starbucks_data <- read_csv("data/starbucks_drinkMenu_expanded.csv")
```

```{r}
ncol(starbucks_data)
nrow(starbucks_data)
```



```{r}
names(starbucks_data)
```


```{r}
glimpse(starbucks_data)
```

## Question 2
Let’s first investigate the calories of different drinks. Select the variables Beverage_category, Beverage, Beverage prep and Calories from your data. Since we are interested in the calorie content, check if there are any NA values in the data, and drop them if there are.

```{r}
  starbucks_data1 <- starbucks_data %>% 
  select(Beverage_category: Calories) %>% 
  filter(is.na(Calories))
starbucks_data1


```

```{r}
starbucks_data <- starbucks_data %>% 
  select(Beverage_category: Calories) %>% 
  filter(!is.na(Calories))
starbucks_data
```

There are no NA values

## Question 3
 Create a new variable (column) called calorie_diff, which stores the difference between 135 calories (135 calories = 10 cubes of sugar!) and the calories in each drink. (hint: you’ll want to subtract the calories from 135 to see which drink have more or less than 10 cups of sugar).
 
```{r}
starbucks_data <- mutate(starbucks_data, calorie_diff = Calories - 135)
starbucks_data_cals <- arrange(starbucks_data, desc(calorie_diff))
starbucks_data_cals 

```

## Question 4
Summarise the mean number of calories in each beverage_category. Which 3 drinks have the most calories? Which 3 drinks have the least? Write a small summary of your findings.
```{r}
mean_beverage_cat <- starbucks_data %>% 
  group_by(Beverage_category) %>% 
  summarise(mean_calories = mean(Calories)) %>% 
  arrange(desc(mean_calories))

mean_beverage_cat
```
Smoothies, Frappuccino® Blended Coffee and Signature Espresso Drinks on average contain the largest amount of calories. Whilst Coffee, Shaken Iced Beverages, Classic Espresso Drinks on average contain the lowest number of calories.

## Question 5

```{r}
mean_beverage_prep <- starbucks_data %>% 
  group_by(Beverage_prep) %>% 
  summarise(mean_calories = mean(Calories)) %>% 
  arrange(desc(mean_calories))

mean_beverage_prep
```

## Question 6
Which Beverage_prep type contains more than the average calories of all drinks?
Hint: to answer this, you’ll have to first figure out what the average calories across all drinks are, and then use that as a filter for the grouped Beverage_prep data.

```{r}
mean_calories_total <- summarise(starbucks_data, mean = mean(Calories))
mean_calories_total
```
Mean calories is 193.8719	

```{r}
mean_beverage_prep %>% 
  filter(mean_calories > 193.8719	)
```

## Question 7
Which is the best type of coffee drink to get if you’re worried about consuming too many calories?

If you are worried about consuming too many calories the best types of coffee drinks to get are the smaller coffee based drinks. These could include Short, Doppio or Solo types or prepped drinks any drinks with milk should be avoided. You should also try to stick Classic Espresso drinks, Coffees or Shaken iced beverages as these on average contain the lowest number of calories. One drink which should certainly be avoided is the White Chocolate Mocha (Without Whipped Cream) made with 2% milk as this contain the equivalent number of calories as 30 cubes of sugar!