---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(broom)
library(modelr)
library(ggfortify)
```

## Question 1

```{r}
project <- read_csv("data/project_management.csv")
head(project)
```

## Question 2

```{r}
plot <- project %>% 
  ggplot() + 
  aes(x = estimated_length, y = actual_length)+
  geom_point()

plot
```

## Question 3

```{r}
project %>% 
  summarise(cor = cor(estimated_length, actual_length))
```

With a correlation coefficient of 0.805 we can say that there is a strong positive correlation 


## Question 4
```{r}
model <- lm(formula = actual_length ~ estimated_length, data = project)

model
```

## Question 5
```{r}
tidy(model)
glance(model)
summary(model)
```

```{r}
autoplot(model)
```

The residual vs fitted does tail off towards the end but there is not a hge variation. Since the p value is less than 0.05 you can say that there is a statically significant relationship.

## Extension

```{r}

autoplot(model)
```

```{r}
plot +
  geom_text(aes(label = 1:nrow(project), hjust = 1.5) )
```
from this 18 looks like it could be a non- influential point
5 looks like it could be an influential point

```{r}
new_model_line <- project %>% 
  filter(X1 != 18) 

new_model <- lm(formula = actual_length ~ estimated_length,
                data = new_model_line
                  )
```

```{r}
new_model
model
```

There is not a significant variation so it would be right to say that this should not be classed as a non_influential outier

```{r}
new_model_line %>% 
  ggplot(aes(x = estimated_length)) +
  geom_point(aes(y = actual_length)) +
  geom_abline(
    intercept = new_model$coefficients[1],
    slope = new_model$coefficients[2],
    col = "red") +
   geom_abline(
    intercept = model$coefficients[1],
    slope = model$coefficients[2],
    col = "blue")
  
  
```


```{r}
autoplot(new_model)
```
```{r}
new_model_line <- project %>% 
  filter(X1 != 5) 

new_model <- lm(formula = actual_length ~ estimated_length,
                data = new_model_line
                  )
```

```{r}

model
new_model

```

There is a significant variation so it would be right to say that this should not be classed as an influential  outier

```{r}
new_model_line %>% 
  ggplot(aes(x = estimated_length)) +
  geom_point(aes(y = actual_length)) +
  geom_abline(
    intercept = new_model$coefficients[1],
    slope = new_model$coefficients[2],
    col = "red") +
   geom_abline(
    intercept = model$coefficients[1],
    slope = model$coefficients[2],
    col = "blue")
  
  
```


```{r}
autoplot(new_model)
```
