---
title: "R Notebook"
output: html_notebook
---

```{r}
library(rpart)
library(rpart.plot)
library(tidyverse)
library(GGally)
library(ggfortify)
library(modelr)
library(tidyverse)
titanic_set <- read_csv('data/titanic_decision_tree_data.csv')

shuffle_index <- sample(1:nrow(titanic_set))

# shuffle the data so class order isn't in order - need this for training/testing split later on 
titanic_set <- titanic_set[shuffle_index, ]
```





```{r}


titanic_clean <- titanic_set %>% 
  filter(!is.na(survived)) %>% 
  mutate(pclass = factor(pclass, levels = c(3,2,1), labels = c("Lower", "Middle", "Upper")),
         embarked = factor(recode(embarked, "C" = "Cherbourg", "Q" = "Queenstown", "S" = "Southampton")),
         age_status = factor(if_else(age <= 16, "child", "adult")),
         survived =  factor(survived, levels = c(0,1), labels = c("No", "Yes")),
         sex = as.factor(sex)) %>% 
  select(-c(X1, passenger_id, name, ticket, fare, cabin, age)) %>% 
 na.omit() %>% 
  as_tibble()
   
summary(titanic_clean)

```

# Question 2
```{r}
#ggpairs(titanic_clean)
```

Passenger class, sex, and age status look to be useful in predicting who isgoing to surevive. 

# Question 3

```{r}
n_data <- nrow(titanic_clean)
test_index <- sample(1:n_data, size = n_data*0.2)
titanic_test  <- slice(titanic_clean, test_index)

# create training set
titanic_train <- slice(titanic_clean, -test_index)
```

```{r}
titanic_test %>% 
  janitor::tabyl(survived)

titanic_train %>% 
  janitor::tabyl(survived)
```

I split 20% because we habe enough data. the splits are also the same so we can go forward and create our decision tree

# Question 4

```{r}
titanic_fit <- rpart(
  formula = survived ~ .,
  data = titanic_train,
  method = "class"
)

rpart.plot(titanic_fit, yesno = 2, fallen.leaves = TRUE, faclen = 6, digits = 4)
rpart.plot(titanic_fit, yesno = 2, fallen.leaves = TRUE, faclen = 6, digits = 4, type = 4, extra = 101)
```

This is saying that women are the most important varibale. If they are a women they have a 75% chance of survinving. If they are male there is only a 21% chance of surviving. It is also clear that 64% of the data are also male.

The next important variable is class for women and  age status for men. For women who are not in lower class have a 92%c chance of surviving



# 6 

```{r}
titanic_test_pred <- titanic_test %>% 
  add_predictions(titanic_fit, type = "class")
```

```{r}
library(caret)

confusionMatrix(titanic_test_pred$pred, titanic_test_pred$survived)
```

The model is 81% accurate. The model is able to identify 95% of the people who died but a much lower ability at ~ 60% to detect people who survived.

# Extension 

```{r}

titanic_fit <- rpart(
  formula = survived ~ .,
  data = titanic_train,
  method = "class", 
  control = rpart.control(minsplit = 500, minbucket = 100)
)

rpart.plot(titanic_fit, yesno = 2, fallen.leaves = TRUE, faclen = 6, digits = 4)

```

```{r}
titanic_test_pred <- titanic_test %>% 
  add_predictions(titanic_fit, type = "class")
```

```{r}
library(caret)

confusionMatrix(titanic_test_pred$pred, titanic_test_pred$survived)
```