```{r}
library(tidyverse)
library(janitor)
library(broom)
library(factoextra)
```

```{r}
customers <- read_csv("mall_customers.csv") %>% 
  clean_names()
```

```{r}
glimpse(customers)
```

```{r}
summary(customers)
```

```{r}
customers %>% 
  ggplot()+ 
  aes(x = annual_income_k, y = spending_score_1_100, colour = gender) + 
  geom_point()
```
It looks like there could be a possible 5 colours with no clear split by gender.


```{r}
customers %>% 
  ggplot()+ 
  aes(x = age, y = spending_score_1_100, colour = gender) + 
  geom_point()
```

```{r}
customers_scaled <- customers %>% 
  select(annual_income_k, spending_score_1_100) %>% 
  mutate_all(scale)
```


```{r}
fviz_nbclust(customers_scaled, kmeans, method = "wss", nstart = 25)
```
5 looks like it could be the best option 
```{r}
fviz_nbclust(customers_scaled, kmeans, method = "silhouette", nstart = 25)
```
Again 5

```{r}
fviz_nbclust(customers_scaled, kmeans, method = "gap_stat")
```

This reccommeds 1 cluster which is not very useful for clustering so we will stick with 5 in this case


```{r}
customer_clusters <- kmeans(customers_scaled,5, nstart = 25)

clusters <- augment(customer_clusters, customers)
```


```{r}
clusters %>% 
  ggplot() + 
  aes(x = annual_income_k, y = spending_score_1_100, colour = .cluster) + 
  geom_point()
```
There are clearly 5 clusters here

low_income, low spending
low_income, high spending
middle earners and spending
high income and low spending
high income and high spending 

```{r}
clusters %>% 
  ggplot()+ 
  aes(x = age, y = spending_score_1_100, colour = .cluster) + 
  geom_point()
```
It also appears that the high spenders are under 40 


```{r}
clusters %>% 
  ggplot()+ 
  aes( y = spending_score_1_100, x = .cluster, fill = gender) + 
  geom_col(position = "dodge")

clusters %>% 
  ggplot()+ 
  aes( y = annual_income_k, x = .cluster, fill = gender) + 
  geom_col(position = "dodge")
```

There doesn't appear to be a significant split by gender in both income and spending score

You could say that cluster 4 are high earners and high spenders, they are also under 40 so you could describe them as young professionals and also around 30

Cluster 2 are low earners and high spending they are also mainly 20-30 they could be grouped as students and financially responsible. 

