---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```

```{r}
tweets <- read_csv("data/code_clan_tweets.csv")
info <- read_csv("data/code_clan_info.csv")
```

```{r}
dim(tweets)
names(tweets)
head(tweets)
```
## Question 2
Find the total number of favourited tweets (stored in favorite_count) that CodeClan tweets have got. Don’t add a tweet’s favorite_count to the total when the tweet was quoted (see the is_quote variable).

```{r}
tweets %>% 
   filter(is_quote == FALSE) %>% 
  summarise(total_favourite_tweets = sum(favorite_count))
  
tweets %>% 
  filter(is_quote == FALSE) %>%
  tally(favorite_count)

```

## Question 3
Summarise the mean number of retweets (retweet_count), split by the type of platform that was used to tweet (source). Again, omit quoted tweets from the mean.
```{r}
tweets %>% 
  filter(is_quote == FALSE) %>% 
  group_by(source) %>% 
  summarise(mean_retweets = mean(retweet_count))
```

## Question 4
Count the total number of likes (i.e. total of favorite_count), split by media type, and arrange them from most likes to least. Assume that any tweets without a listed media type are of type “text”.

```{r}
tweets %>% 
  mutate(media_type = coalesce(media_type, "text")) %>% 
  group_by(media_type) %>% 
  summarise(total_likes = sum(favorite_count))
  
```

## Question 5

Find the mean number of characters that a CodeClan tweet contains.
```{r}
tweets %>% 
  summarise(mean_character_count = mean(display_text_width))
```

## Question 6
The code_clan_info.csv data file contains status_url along with other info. Load this in, and join it to the code_clan_tweets tibble, so that you have a status_url for each tweet. Decide which variable to join the tibbles on.

```{r}
head(info)
head(tweets)
```


```{r}
tweets_url <- tweets %>% 
  left_join(info, by = "tweet_id")
```

## Question 7 
From your new joined data, create a new tibble codeclan_hashtags containing only the tweet_id and hashtags in lowercase for analysis. Keep only those tweets with hashtags.

```{r}
codeclan_hashtags <- tweets_url %>% 
  select(tweet_id, hashtags) %>% 
  mutate(hashtags = str_to_lower(hashtags)) %>% 
  drop_na()

codeclan_hashtags
```
Some tweets have more than one hashtag, denoted by the c( symbols at the start of the string. Use the str_sub() and str_detect() functions and your codeclan_hashtags tibble from above to find all the cases in which the hashtag string begins with characters c(.

```{r}
codeclan_hashtags %>% 
  mutate(first_letters = str_sub(hashtags, 1, 2)) %>% 
  mutate(first_letters = str_detect(first_letters, "c\\(")) %>% 
  filter(first_letters == TRUE) %>% 
  select(-first_letters)

```
## Question 9 
Use the str_detect() function to find all tweets with text that mentions “Edinburgh”, and count how many such tweets there are.

```{r}
tweets %>% 
  mutate(str_detect = str_detect(text, "[Ee]dinburgh")) %>% 
           filter(str_detect == T) %>% 
  summarise(total = n())
 
```
## Question 10
Use str_extract_all() with a regular expression to find out which Twitter users CodeClan have been tweeting

```{r}
tweets %>%  
  mutate(tweeters = str_extract_all(text, "@[A-z_]{1,15}")) %>% 
  select(tweeters, text) %>% 
 pull(tweeters)

```


```{r}
tweets %>%  
  mutate(tweeters = str_extract_all(text, "(^|[^@\\w])@(\\w{1,15})\\b")) %>% 
  select(tweeters, text) %>% 
 pull(tweeters)

```