---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```

```{r}
tweets <- read_csv("data/code_clan_tweets.csv")
info <- read_csv("data/code_clan_info.csv")
```

```{r}
dim(tweets)
names(tweets)
head(tweets)
```
## Question 2
Find the total number of favourited tweets (stored in favorite_count) that CodeClan tweets have got. Don’t add a tweet’s favorite_count to the total when the tweet was quoted (see the is_quote variable).

```{r}
tweets %>% 
   filter(is_quote == FALSE) %>% 
  summarise(total_favourite_tweets = sum(favorite_count))
  
tweets %>% 
  filter(is_quote == FALSE) %>%
  tally(favorite_count)

```

## Question 3
Summarise the mean number of retweets (retweet_count), split by the type of platform that was used to tweet (source). Again, omit quoted tweets from the mean.
```{r}
tweets %>% 
  filter(is_quote == FALSE) %>% 
  group_by(source) %>% 
  summarise(mean_retweets = mean(retweet_count))
```

## Question 4
Count the total number of likes (i.e. total of favorite_count), split by media type, and arrange them from most likes to least. Assume that any tweets without a listed media type are of type “text”.

```{r}
tweets %>% 
  mutate(media_type = coalesce(media_type, "text")) %>% 
  group_by(media_type) %>% 
  summarise(total_likes = mean(favorite_count))
  
```

## Question 5

Find the mean number of characters that a CodeClan tweet contains.
```{r}
tweets %>% 
  summarise(mean_character_count = mean(display_text_width))
```

## Question 6
The code_clan_info.csv data file contains status_url along with other info. Load this in, and join it to the code_clan_tweets tibble, so that you have a status_url for each tweet. Decide which variable to join the tibbles on.

```{r}
head(info)
head(tweets)
```


```{r}
tweets_url <- tweets %>% 
  left_join(info, by = "tweet_id")
```

