---
title: "R Notebook"
output: 
  html_notebook: 
    toc: yes
    theme: paper
---

```{r}
library(tidyverse)
library(corrr)
library(ggfortify)
library(GGally)
library(modelr)
library(relaimpo)
```



```{r}
house_data <- read_csv("data/kc_house_data.csv")
```

```{r}
glimpse(house_data)

house_data %>% 
  summarise_all(~(sum(is.na(.))))
```

id - Unique ID for each home sold
date - Date of the home sale
price - Price of each home sold
bedrooms - Number of bedrooms
bathrooms - Number of bathrooms, where .5 accounts for a room with a toilet but no shower
sqft_living - Square footage of the apartments interior living space
sqft_lot - Square footage of the land space
floors - Number of floors
waterfront - A dummy variable for whether the apartment was overlooking the waterfront or not
view - An index from 0 to 4 of how good the view of the property was
condition - An index from 1 to 5 on the condition of the apartment,
grade - An index from 1 to 13, where 1-3 falls short of building construction and design, 7 has an average level of construction and design, and 11-13 have a high quality level of construction and design.
sqft_above - The square footage of the interior housing space that is above ground level
sqft_basement - The square footage of the interior housing space that is below ground level
yr_built - The year the house was initially built
yr_renovated - The year of the house’s last renovation
zipcode - What zipcode area the house is in
lat - Lattitude
long - Longitude
sqft_living15 - The square footage of interior housing living space for the nearest 15 neighbors
sqft_lot15 - The square footage of the land lots of the nearest 15 neighbors


```{r}
house_data <- house_data %>% 
  dplyr::select(-c(id, date, sqft_living15, sqft_lot15, zipcode))
```


```{r}
house_data <- house_data %>% 
  mutate(waterfront = as.logical(waterfront))
```

```{r}
house_data <- house_data %>% 
  mutate(renovated = yr_renovated > 0 ) %>% 
  dplyr::select(- yr_renovated)
```

```{r}
house_data <- house_data %>% 
  mutate(across(view:grade,  factor))

glimpse(house_data)
```

```{r}
alias(lm(formula = price ~ ., data = house_data))
```
```{r}
house_data <- house_data %>% 
  dplyr::select(-sqft_basement)

alias(lm(formula = price ~ ., data = house_data))
```
```{r message=TRUE, warning=TRUE}
house_data_numeric <- house_data %>% 
  dplyr::select(is.numeric)

house_data_nonnumeric <- house_data %>% 
  dplyr::select(price, !is.numeric)


```

```{r message=FALSE, warning=FALSE}
ggpairs(house_data_numeric)
```

```{r message=FALSE, warning=FALSE}
ggpairs(house_data_nonnumeric)
```
```{r}
mod1a <- lm(price ~ sqft_living, data = house_data)

autoplot(mod1a)

summary(mod1a)
```

```{r}
mod1b <- lm(price ~  grade  , data = house_data)

autoplot(mod1b)

summary(mod1b)
```

mod1b is probably the best here


```{r}
residual_house_data <- house_data %>% 
  add_residuals(mod1b) %>% 
  dplyr::select(- c(price, grade))  

res_data_numeric <- residual_house_data %>% 
  dplyr::select(is.numeric)

res_data_nonnumeric <- residual_house_data %>% 
  dplyr::select( resid, !is.numeric)



```

```{r}
ggpairs(res_data_numeric)
```

```{r}
ggpairs(res_data_nonnumeric)
```

## Model 2
```{r}
mod2a <-  lm(price ~ grade + sqft_living, data = house_data)

autoplot(mod2a) 

summary(mod2a)
```
```{r}
mod2b <- lm(price ~ grade + waterfront, data = house_data)

autoplot(mod2b) 

summary(mod2b)
```

mod2a is the better option here

```{r}

residual_house_data <- house_data %>% 
  add_residuals(mod2a) %>% 
  dplyr::select(- c(price, grade, sqft_living))  

res_data_numeric <- residual_house_data %>% 
  dplyr::select(is.numeric)

res_data_nonnumeric <- residual_house_data %>% 
  dplyr::select( resid, !is.numeric)



```


```{r message=FALSE, warning=FALSE}
ggpairs(res_data_numeric)
ggpairs(res_data_nonnumeric)
```

```{r}

```

```{r}
mod3a <- lm(price ~ grade + sqft_living + lat, data = house_data)
autoplot(mod3a)
summary(mod3a)
```
```{r}
mod3b <- lm(price ~ grade + sqft_living + waterfront, data = house_data)
autoplot(mod3b)
summary(mod3b)
```

```{r}
mod3c <- lm(price ~ grade + sqft_living + view, data = house_data)
autoplot(mod3c)
summary(mod3c)
```
mod3a

```{r}

residual_house_data <- house_data %>% 
  add_residuals(mod3a) %>% 
  dplyr::select(- c(price, grade, sqft_living, lat))  

res_data_numeric <- residual_house_data %>% 
  dplyr::select(is.numeric)

res_data_nonnumeric <- residual_house_data %>% 
  dplyr::select( resid, !is.numeric)



```


```{r message=FALSE, warning=FALSE}
ggpairs(res_data_numeric)
ggpairs(res_data_nonnumeric)
```


```{r}
mod4a <- lm(price ~ grade + sqft_living + lat + yr_built, data = house_data)

autoplot(mod4a)

summary(mod4a)
```
```{r}
mod4b <- lm(price ~ grade + sqft_living + lat + waterfront, data = house_data)

autoplot(mod4b)

summary(mod4b)
```


```{r}
mod4c <- lm(price ~ grade + sqft_living + lat + view, data = house_data)

autoplot(mod4c)

summary(mod4c)
```

```{r}
anova(mod3a, mod4c)
```

mod4c

## Extension 

 grade:sqft_living  
 
 
```{r}
mod5a <- lm(price ~ grade + sqft_living + lat + view + grade:sqft_living, data = house_data)

autoplot(mod5a)

summary(mod5a)
```

grade:lat
```{r}
mod5b <- lm(price ~ grade + sqft_living + lat + view + grade:lat, data = house_data)



summary(mod5b)
```

grade:waterfront
```{r}
mod5c <- lm(price ~ grade + sqft_living + lat + view + grade:waterfront, data = house_data)



summary(mod5c)
```
sqftliving:lat

```{r}
mod5d <- lm(price ~ grade + sqft_living + lat + view + sqft_living:lat, data = house_data)



summary(mod5d)
```

sqftliving:waterfront
```{r}
mod5e <- lm(price ~ grade + sqft_living + lat + view + sqft_living:waterfront, data = house_data)



summary(mod5e)
```
lat:waterfront

```{r}
mod5f <- lm(price ~ grade + sqft_living + lat + view + lat:waterfront, data = house_data)



summary(mod5f)
```


mod5c is the best fit 

```{r}
anova(mod4a, mod5c)


anova(mod5c, mod4a)
```


```{r}
calc.relimp(mod4c, type = "lmg", rela = TRUE)
```

