---
title: "R Notebook"
output: html_notebook
---
```{r}
library(tidyverse)
library(ggthemes)
backpack <- CodeClanData::backpack
```
# MVP
## Question 1
Load in the libraries you need, and look at the backpack data. Take note of variable names and dimensions.

```{r}

backpack <- backpack %>% 
  mutate(back_problems = as.logical(back_problems))
dim(backpack)
glimpse(backpack)
```

## Question 2
What is the distribution of backpack weights that students are carrying? Choose an appropriate graph to show the distribution.

```{r}
ggplot(backpack) +
  aes(x = backpack_weight) +
  geom_histogram( fill = "blue", colour = "black", bins = 27, alpha = 0.5) +
  geom_density(aes(y = ..count..)) + 
  labs(
    x = "Backpack Weight (lbs)",
    y = "Count",
    title = "Distribution of backpack weights"
  ) +
  scale_y_continuous(breaks = 0:20)
```

From the graph we can see that the majority of backpack weight fall below 15lbs. However there is one outlier of over 30 lbs.

## Question 3
Are there differences in backpack weight between sex?
```{r}
ggplot(backpack) +
  aes(x = backpack_weight) +
  geom_histogram( colour = "black", bins = 30, aes(fill = sex)) +
  geom_density(aes(y = ..count..)) +
  facet_wrap(~ sex, ncol  = 1) +
  labs(
    x = "Backpack Weight (lbs)",
    y = "Count",
    title = "Distribution of backpack weights by sex"
  ) +
  scale_y_continuous(breaks = 0:13) 
 

```

We can see that more females have lighter backpacks, whilst males tend to have a more even distribution of back packs

## Question 4
What is the relationship between body weight and backpack weight?
```{r}
ggplot(backpack) +
  aes(x= backpack_weight, y = body_weight) +
  geom_point(colour = "blue") +
  labs(x = "Backpack weight (lbs)",
       y = "Body weight(lbs)",
       title = "Plot of Body Weight Over Backpack Weight")
```
 THere is no clear relationship between backpack weight and bodyweight
 
## Question 5
Is this relationship different between men and women? Choose an appropriate plot and interpret your findings.

```{r}
ggplot(backpack) +
  aes(x= backpack_weight, y = body_weight,colour = sex) +
  geom_point() +
  labs(x = "Backpack weight (lbs)",
       y = "Body weight(lbs)",
       title = "Plot of Body Weight Over Backpack Weight by Sex")
```

Again there is no obviously relationshop between men and women. Women tend to have a heavier backpack for their bodyweight.


## Question 6
What proportion of students report back pain?
```{r}
backpack %>% 
  mutate(back_problems = as.logical(back_problems)) %>% 
  ggplot() +
  aes(x= back_problems) +
  geom_bar(fill = "blue") +
  labs(
    x = "Back problems",
    y = "number of people",
    title = "Proportion of People with Back Problems"
  )
 
```

As we can see the majoity of people do not suffer from back problem 

```{r}
backpack %>% 
  mutate(back_problems = ifelse(back_problems == TRUE, "Yes", "No")) %>% 
  group_by(back_problems) %>% 
  summarise(count = n()) %>% 
  ggplot() +
  aes(x="", y = count, fill = back_problems) +
  coord_polar("y", start=0) +
  geom_bar(stat = "identity") +
  labs(
    fill = "Back Problems",
    title = "Proportion of People with Back Problems"
  ) +
  theme_void()
 
```

## Question 7.

Is this proportion different between men and women?

```{r}

  ggplot(backpack) +
  aes(x= back_problems) +
  geom_bar(fill = "light blue") +
  labs(
    x = "Back problems",
    y = "number of people",
    title = "Proportion of People with back problems"
  ) +
  facet_wrap(~ sex)
 
 
```
```{r}
backpack %>% 
mutate(back_problems = ifelse(back_problems == TRUE, "Yes", "No")) %>% 
  group_by(back_problems, sex) %>% 
  summarise(count = n()) %>% 
  ggplot() +
  aes(x= "" , y = count, fill = back_problems ) +
  geom_col( position = "fill") +
  labs(
    x = "Back problems",
    y = "number of people",
    title = "Proportion of People with back problems"
  ) +
  facet_wrap(~ sex)
 
 
```



## Question 8
Now you’ve investigated your data separately, create plots to describe the relationship between backpack weight, body weight, gender and reported backpain.

Try both backpack_weight and body_weight as well as the ratio.

```{r}

ggplot(backpack) +
  aes(x= backpack_weight, y = body_weight) +
  geom_point(colour = "blue") +
  labs(x = "Backpack weight (lbs)",
       y = "Body weight(lbs)",
       title = "Plot of Body Weight Over Backpack Weight") + 
  facet_grid(sex ~ back_problems, labeller = "label_both" )


```

```{r}
ggplot(backpack) +
  aes(x= ratio) +
area(stat = "bin") + 
  facet_grid(sex ~ back_problems, labeller = "label_both")

```

THere dpes not appear to be any correlation between male, female or back problems 
# Extension 
## Question 1

Does reported backpain differ across the year groups? Ignore year 0 in your data.
```{r}
backpack %>% 
  filter(year > 0) %>% 
  mutate(year = as.character(year)) %>% 
   ggplot() +
  aes(x= back_problems, fill = year) +
  geom_bar( position = "dodge") + 
  labs(
    x = "Back Problems",
    y = "Number of People",
    title = "Proportion of People with back problems",
    fill = "Year")
``` 
From  this graph, third and fourth years tend to have the highest proption of back problesm

# Question 2.

Is there a difference between how heavy the bags those in different years carry?

```{r}
backpack %>% 
  filter(year > 0) %>% 
  mutate(year = as.character(year)) %>% 
ggplot() + 
  aes(y = backpack_weight,  x = year, fill = year) +
  geom_boxplot() +
  labs(
    x = "Year",
    y = "Backpack Weight",
    title = "Backpack Weights by Year Group,
    fill = "Year")
```

