---
title: "R Notebook"
output: html_notebook
---
```{r}
library(tidyverse)
library(janitor)
library(infer)
library(car)
```
# 1.Load the data again, clean_names(), and re-familiarise yourself with it
```{r}
ames <- read_csv("data/ames.csv") %>% 
  clean_names()
```

# 2.Investigate the distribution of lot_area. Is the distribution roughly normal? If not, what problems do you find?

```{r}
ames %>% 
  ggplot() + 
  aes(x = lot_area) +
  geom_histogram(col = "white")


qqPlot(ames$lot_area)
```

It seems that it is hugely left skewed> it looks like for the large part that the majority of the data fits a normal distribution. However there are some that there are some which fall outside  the distribution

# 3. Investigate the distribution of lot_area. Is the distribution roughly normal? If not, what problems do you find?
```{r}
bootstrap <- ames %>% 
  specify(response = lot_area) %>% 
  generate(reps = 5000, type = "bootstrap") %>% 
  calculate(stat = "mean")
```

```{r}
bootstrap %>% 
  ggplot() + 
  aes(x = stat) +
  geom_histogram()
```

```{r}
infer_ci_95 <- bootstrap %>% 
  get_ci(level = 0.95, type = "percentile")

infer_ci_95
```

```{r}
bootstrap %>% 
  visualise(bins =30) +
  shade_ci(endpoints = infer_ci_95)
```

```{r}
infer_ci_99 <- bootstrap %>% 
  get_ci(level = 0.99, type = "percentile")

infer_ci_99
```

```{r}
bootstrap %>% 
  visualise(bins =30) +
  shade_ci(endpoints = infer_ci_99)
```

```{r}
bootstrap %>% 
  summarise(mean(stat))
```

# Extension 
```{r}
year_built <- ames %>% 
  select(year_built) %>% 
  mutate(before_1920 = year_built < 1920) %>% 
  mutate(before_1920 = as.numeric(before_1920))
```

```{r}
yb_bootstrap <- year_built %>% 
   specify(response = before_1920) %>% 
  generate(reps = 200, type = "bootstrap") %>% 
  calculate(stat = "mean")

 yb_bootstrap %>% 
  get_ci(level = 0.95, type = "percentile")

yb_bootstrap %>% 
 summarise( mean(stat))
```
```{r}
yb_bootstrap <- year_built %>% 
   specify(response = before_1920) %>% 
  generate(reps = 50000, type = "bootstrap") %>% 
  calculate(stat = "mean")

 yb_bootstrap %>% 
  get_ci(level = 0.95, type = "percentile")

yb_bootstrap %>% 
 summarise( mean(stat))
```
The number of reps does not matter too much 

```{r}
yb_bootstrap <- ames %>% 
   specify(response = year_built, success = 1920)  %>% 
  generate(reps = 200, type = "bootstrap") %>% 
  calculate(stat = "prop")

 yb_bootstrap %>% 
  get_ci(level = 0.95, type = "percentile")

yb_bootstrap %>% 
 summarise( mean(stat))
```